---
title: "Homework 1, Onyeka Isamah"
output: github_document
---


# Attaching Tidyverse

```{r setup}
library (tidyverse)
```

# Problem 1: 

  Creating a data frame using Tibble

```{r dataframe_tibble, echo=FALSE}
    homework1_df = tibble (
    vec_numeric = rnorm(10)
,   vec_char = c("Wendy", "Kevin", "Fred", "Jeff", "Leslie", "Jen", "Michelle", "Emily", "Jake", "Sam"),
    vec_logical = c("TRUE", "TRUE", "TRUE", "FALSE", "TRUE", "TRUE", "TRUE", "FALSE", "TRUE", "TRUE"),
    vec_factor = factor (c("work", "home", "mobile", "work", "home", "mobile", "work", "home", "mobile", "home")))
```


```{r print tibble, echo=FALSE}
  homework1_df
```

## Taking the mean using the pull function 


```{r means using pull}
  mean(pull (homework1_df, var = vec_numeric))
  mean(pull(homework1_df, var = vec_char))
  mean(pull(homework1_df, var = vec_logical))
  mean(pull(homework1_df, var = vec_factor))
```

## 

  Taking the mean for the numeric variable in the data frame worked, but taking the mean for the     logical,  character, and factor variables did not work.


# Using the as.numeric function to convert variable
  I believe that the as.numeric function worked for vec_factor because this variable has a has 3 different "levels". The numbers assigned are now coded as 1,2, or 3. 
  
  When trying to convert vec_char and vec_logistical, I get a warning message that says "NAs introduced by coercion". #
  
```{r As Numeric Function, eval=FALSE}

  x <- as.numeric(pull(homework1_df, vec_factor))
  mean(x)

  y <- as.numeric(pull(homework1_df, vec_char))
  mean(y)

  z <- as.numeric(pull(homework1_df, vec_logical))
  mean(z)
```



# Problem 2 
  Penguins Dataset

```{r Opening penguins data}
  data("penguins", package = "palmerpenguins")
```

  [Using view, ncol, and nrow in the console]
  
  The dataset 'penguins' has 344 observations and 8 variables. Using ncol = 8 and nrow = 344. The     variables include:
  
  (3)Species: Adele, Chinstrap, Gentoo
  
  (3)Islands: Biscoe, Dream, Torgersen
  
  Bill length, mm
  
  Bill depth, mm
  
  Flipper length, mm
  
  Body Mass, g
  
  Sex: M/F
  
  Year, 2007 -2009
  
  
  The mean flipper length is 201 mm. 
  


## 
  Creating scatterplot 'penguinplot' using ggplot, with color
  
  Saving scatter plot
  
  Exporting scatterplot into a PDF file

```{r Scatterplot, echo=FALSE, warning=FALSE}

  penguinplot <- ggplot (penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

  ggsave(penguinplot, filename = "penguinplot.pdf")
```
```{r Print Plot, echo=FALSE}
  penguinplot
```


