---
title: "Homework 1, Onyeka Isamah"
output: github_document
---

# Attaching Tidyverse

```{r setup}
library (tidyverse)
```

# Problem 1: 

Creating a data frame using Tibble

```{r dataframe_tibble, echo=FALSE}
  homework1_df = tibble (
    vec_numeric = rnorm(10)
,    vec_char = c("Wendy", "Kevin", "Fred", "Jeff", "Leslie", "Jen", "Michelle", "Emily", "Jake", "Sam"),
    vec_logical = c("TRUE", "TRUE", "TRUE", "FALSE", "TRUE", "TRUE", "TRUE", "FALSE", "TRUE", "TRUE"),
    vec_factor = factor (c("work", "home", "mobile", "work", "home", "mobile", "work", "home", "mobile", "home")))
```


```{r print tibble, echo=FALSE}
homework1_df
```

## Taking the mean using the pull function 


```{r means using pull}
mean(pull (homework1_df, var = vec_numeric))
mean(pull(homework1_df, var = vec_char))
mean(pull(homework1_df, var = vec_logical))
mean(pull(homework1_df, var = vec_factor))
```

## 

  Taking the mean for the numeric variable in the data fram worked, but taking the mean for the     logical,  character, and factor did not work.


# Using the as.numeric function to convert variable
  I believe that the as.numeric function worked for vec_factor because this variable has a has 3 different "levels". The numbers assigned are now coded as 1,2, or 3. 
  
  When trying to convert vec_char and vec_logistical, I get a warning message that says "NAs introduced by coercion". #
  
```{r As Numeric Function, eval=FALSE}
x <- as.numeric(pull(homework1_df, vec_factor))
mean(x)

y <- as.numeric(pull(homework1_df, vec_char))
mean(y)

z <- as.numeric(pull(homework1_df, vec_logical))
mean(z)
```